---
title: "Python In Rstudio"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare system

I will be working with the retigulate package but when doing this,

Python will be used in a python environment.
without intervention it will be build in the root of your system `Sys.getenv("HOME")`.
This is not generally desirable, thus it can be changed by changing the .Renvironment.

Open the r_environment file with: `usethis::edit_r_environ()` 
Set the `WORKON_HOME` property to what you want.

```{r, eval=FALSE}
WORKON_HOME = "Path/To/Desired/Folder"
```

You can also choose your desired version of python.
Currently my system uses the version of python in the r-retigulate directory automatically created by the package.
But you can change the default behaviour using:

```{r, eval=FALSE}
#https://stackoverflow.com/questions/49738564/r-set-environment-variable-permanently
RETICULATE_PYTHON = "/usr/local/bin/python3"
```

I do not know how this work alongside the python interpreter selection in the global options.

## download package.

To use Python in R studio you create a python environment.
On my personal pc it was enough to download the `reticulate` package.

```{r, eval=FALSE}
install.packages("retigulate")
reticulate::repl_python()
```

Now you are in python.

### .py

When working in .py files the package will automatically take over.
(in my experience so far)

## Further reading

The current set up allows for python in r studio, but a lot more information is availeble [here](https://rstudio.github.io/reticulate/index.html "Github page Retigulate").

The package is way more powerful then shown till now.
For example it is able to:

- run python in r scripts.
- Convert objects from one language to the other. 
- be added to packages,
- implemented in R markdown.
